Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-22 Paper.tex
Add description of the new Byzantium precompiles to section 8.

As can be seen, there are four exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are four so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The four contracts in addresses 1, 2, 3 and 4 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme, the RIPEMD 160-bit hash scheme and the identity function respectively.

>>>>

As can be seen, there are eight exceptions to the usage of the general execution framework $\Xi$ for evaluation of the message call: these are eight so-called `precompiled' contracts, meant as a preliminary piece of architecture that may later become \textit{native extensions}. The eight contracts in addresses 1 to 8 execute the elliptic curve public key recovery function, the SHA2 256-bit hash scheme, the RIPEMD 160-bit hash scheme, the identity function, arbitrary precision modular exponentiation, elliptic curve addition, elliptic curve scalar multiplication and an elliptic curve pairing check respectively.
